### 2013-11-06 proposal/proposal/chapter5.tex
Changes

\begin{itemize}
\item Analysing other cooperative solution concepts such as Kernel and Nucleolus where payoff division is guaranteed to exist but may have optimal results.
\item Applying Weighted Voting Games (WCG) type of valuation function in our scenarios, Developing a multiple weighted algorithm to find best coalition structures satisfying different weights on each community.
\item Implementing Q-learning and reinforcement learning technique and also a tic-tac-toe based repeated game technique for individual Web Service decision making process, in long term and repeated game scenarios.
\item Developing a community membership algorithm technique for our agents in "incomplete information" settings.
\end{itemize}
Answering these questions is undoubtedly complex. Therefore, we do not expect a comprehensive answer to all these questions.

>>>>

\begin{itemize}
\item Analysing other cooperative solution concepts such as Kernel and Nucleolus where payoff division is guaranteed to exist but may have optimal results.
\item Applying Weighted Voting Games (WCG) type of valuation function in our scenarios, Developing a multiple weighted algorithm to find best coalition structures satisfying different weights on each community.
\item Implementing Q-learning and reinforcement learning technique and also a tic-tac-toe based repeated game technique for individual Web Service decision making process, in long term and repeated game scenarios.
\item Developing an approximation algorithm for shapely value payoff distribution vector in community of service setting.    
\item Developing a community membership algorithm technique for our agents in "incomplete information" settings.
\item Developing an open source, Java based Tool, with UI for solving Core and Shapely solution concepts based on different input valuation functions.
\end{itemize}
